%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% Preface
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\chapter{Preface}
\thispagestyle{empty}

It is baffling to myself that I am writing a book to detail the beauty of human nature as I experience it through my lens, and the irony of this situation has not escaped me.

\bigskip
And it is a given that my definition of beauty is like none other.

\bigskip
This is not a self-help book nor is it a memoir of my experience, and it is also not a book on any expertise. This is simply a cheap condensation and imitation of the experiences I have gained and stolen when interacting with the world. The purpose of this book is mainly for me to demonstrate the concept of transience and passively work towards making the world slightly more liveable for me.

\bigskip
I came up with this title by chance, as there were no particular other word combination that sounded appropriate. Of course, the subtitle is a reference to a particular card, its meaning, and my own way of seeing the world. There is nowhere else where you can find a lifeform which actively despises affection, yet can still comprehend and demonstrate affection and have feelings.

\bigskip
I do not hope that anyone will be reading these words. In fact, my hope is that this garbage work catches no one's attention and never impresses anybody. Only when that day comes will I be able to truly experience common sense.

\bigskip
At any rate, welcome to my world of normalcy, where things happen simply as they are.

\vfill
\begin{flushright}
Whitelion\\
\today
\end{flushright} 